Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2019-02-12 paper/ms.tex
Declaring this commit a first draft of Carlyn's paper.

{\color{red} ARE THE BELOW NUMBERS CORRECT?}
The C-O and C-O-Ne models have the same central density
and temperature $7 \times 10^8$~K, respectively.
The C-O model had core composition of (\C{12} = 0.4, 
\Ne{20} = 0.03, \Ox{16} = 0.57) and envelope composition 
of (\C{12} = 0.5, \Ne{20} = 0.02, \Ox{16} = 0.48). 
The C-O-Ne model had core composition of (\C{12} = 0.X, 
\Ne{20} = 0.XX, \Ox{16} = 0.XX) and envelope composition 
of (\C{12} = 0.XX, \Ne{20} = 0.0X, \Ox{16} = 0.XX). 
The profiles of the two-dimensional models match those of
the one-dimensional models (shown in \figref{fig:init_conds})
up to very slight errors from the mapping process. {\color{red}
OMIT THIS LAST SENTENCE? DONT HAVE A FIGURE}

@@

We frame the presention of the results of the suites of simulations 
principally in terms of the yield of \Ni{56}, the source of 
the light curve of an event. \Ni{56} thus serves as a proxy
for the brightness of an explosion and comparison of the yields
is equivalent to comparing the brightness events. The
yields estimated from $Y_e$ and the NSE progress
variable, by assuming the composition in NSE is \Ni{56} plus equal
parts \Fe{54} and \Ni{58}, as described in
\citet{townetal2009,Meaketal09}.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_cum_dist.pdf}
\caption{\label{fig:cumdist}
The cumulative distribution of the \Ni{56} yield for explosions from
C-O and hybrid C-O-Ne models. The hybrid results are shown in red, and the CO
results are shown in blue. The curve for the hybrid models is shifted 
to the left, indicating that explosions from hybrid progenitors produce
less \Ni{56} than explosions from traditional C-O models. 
}
\end{figure}
The cumulative distribution of the \Ni{56} yield for explosions from
C-O and hybrid C-O-Ne models is presented in \ref{fig:cumdist}. 
The figure shows that the hybrid models consistenly have a higher
cumulative fraction at a given mass of \Ni{56}, which indicates
that the yields of \Ni{56} are consistenly lower in explosions 
from hybrid progenitors. {\color{red} CHECK/EXPAND THIS}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_vs_mass_at_high_dens.pdf}
\caption{\label{fig:masshighdens}
Final estimated IGE {\color{red} 
TO BE SURE- NOT \Ni{56} AS FIGURE IS LABELED?} yield 
vs.\ mass {\color{red} above} $2\times 10^7~\grampercc$
at the time of the first DDT in a simulation.  Individual 
realizations are shown (C-O-NE
progenitors in red, C-O in blue) along with rectangles of length
$\pm 1 \sigma$ along each axis and centered at their average values 
for C-O and C-O-Ne.
}
\end{figure}

Figure \ref{fig:masshighdens} compares the final yield of IGE elemets
for the C-O and C-O-Ne simulation suites with the amount of expansion of the
WD during the deflagration phase. The amount of expansion is 
characterized by the mass above $2 \times 10^7~\grampercc$ at the 
time of the DDT, with more high-density mass
indicating less expansion during deflagration. The averages of both
the C-O and C-O-Ne suites along both axes are indicated by the shaded
regions with $\pm1\sigma$ widths.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/FMBTI_v_Ni56Yield_plot.pdf}
\caption{\label{fig:conversion}
	The conversion of \Ni{56} to IGEs are more pronounced in my case. There are two assumptions as to why figure 6 is more pronounced in my paper then in Dons. 
First is that higher critical density leads to higher electron capture resulting in less Ni56 produced. Figure 4 shows that CO model has a stronger electron capture then the hybrid model. The second is that the central ignition leads to early burning at higher density. Both of these cases lead to more electron capture resulting in a larger difference in evolution between the models.
NEW: Production of 56Ni and mass burned to IGEs for CO (red) and
hybrid CONe (green) WD realizations. SAME AS DON'S FIG 18
}
\end{figure}
Figure \ref{fig:conversion} shows the estimated \Ni{56} yields 
across the range of masses burned to IGE
for all C-O and C-O-Ne realizations at the end 
of the simulaitons ($4.0$~\second),
at which point the total mass burned to \Ni{56} had become constant.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/compare_ratio_v2.png}
\caption{\label{fig:compare_ratio}
Figure 8 shows the evolution of the materials for both models. It is determined that the CO model had the greatest amount of Ni56, then the other IGE materials, compared to the hybrid model.  
SAME AS DON'S FIGURE 19.
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/compare_burned_mass_v2.png}
\caption{\label{fig:compare_burned}
SAME AS DON'S FIGURE 20.
C/O blue hybrid red.
Note that one of the C/O simulations presented did not complete.
}
\end{figure}

@@

The conversion of \Ni{56} to Iron group elements are more pronounced in my
case. There are two assumptions as to why figure 6 is more pronounced
in my paper then in Dons.  First is that higher critical density leads
to higher electron capture resulting in less \Ni{56} produced. The second
is that the central ignition leads to early burning at higher density.

As the star burns mass, the surface area grows, resulting in a decrease
in density. The results show that the models that burned less mass during
the deflagration phase, expand less, produce more \Ni{56}. This is because
the density rich mass the model has at the DDT point is the ‘fuel’
it needs to produce \Ni{56}. Therefore, the more mass, the more Ni-56. On
average, the CO model, shown in figure 4, reaches the DDT faster then
the hybrid model. Figures 3 and 4 show that the hybrid model has a wider
range of estimated \Ni{56} mass suggesting a greater range of burned mass
and expansion during the deflagration phase.

>>>>

{\color{red} THE BELOW NUMBERS NEED SORTING OUT!}
The C-O and C-O-Ne models has the same central temperature
and density ????
The C-O models had a central density and 
temperature of $4.62 \times 10^{9}$ $4.27 \times 10^{9}$ ???
and $7 \times 10^8$~K, respectively.
The C-O model had core composition of (\C{12} = 0.4, 
\Ne{20} = 0.03, \Ox{16} = 0.57) and envelope composition 
of (\C{12} = 0.5, \Ne{20} = 0.02, \Ox{16} = 0.48). 
The C-O models had a central density and 
temperature of $4.62 \times 10^{9}$ 
and $8.07 \times 10^8$~K, respectively.
The C-O-Ne model had core composition of (\C{12} = 0.X, 
\Ne{20} = 0.XX, \Ox{16} = 0.XX) and envelope composition 
of (\C{12} = 0.XX, \Ne{20} = 0.0X, \Ox{16} = 0.XX). 
The profiles of the two-dimensional models match those of
the one-dimensional models (shown in \figref{fig:init_conds})
up to very slight errors from the mapping process. {\color{red}
OMIT THIS LAST SENTENCE? DONT HAVE A FIGURE}

@@

We frame the presentation of the results of the suites of simulations 
principally in terms of the yield of \Ni{56}, the source of 
the light curve of an event. \Ni{56} thus serves as a proxy
for the brightness of an explosion and comparison of the yields
is equivalent to comparing the brightness events. The
yields estimated from $Y_e$ and the NSE progress
variable, by assuming the composition in NSE is \Ni{56} plus equal
parts \Fe{54} and \Ni{58}, as described in
\citet{townetal2009,Meaketal09}.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_cum_dist.pdf}
\caption{\label{fig:cumdist}
The cumulative distribution of the \Ni{56} yield for explosions from
C-O and hybrid C-O-Ne models. The hybrid results are shown in red, and the CO
results are shown in blue. The curve for the hybrid models is shifted 
to the left, indicating that explosions from hybrid progenitors produce
less \Ni{56} than explosions from traditional C-O models. 
}
\end{figure}
The cumulative distribution of the \Ni{56} yield for explosions from
C-O and hybrid C-O-Ne models is presented in \ref{fig:cumdist}. 
The figure shows that the hybrid models consistently have a higher
cumulative fraction at a given mass of \Ni{56}, which indicates
that the yields of \Ni{56} are consistently lower in explosions 
from hybrid progenitors. {\color{red} CHECK/EXPAND THIS}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_vs_mass_at_high_dens.pdf}
\caption{\label{fig:masshighdens}
Final estimated IGE {\color{red} 
TO BE SURE- NOT \Ni{56} AS FIGURE IS LABELED?} yield 
vs.\ mass {\color{red} above} $2\times 10^7~\grampercc$
at the time of the first DDT in a simulation.  Individual 
realizations are shown (C-O-Ne
progenitors in red, C-O in blue) along with rectangles of length
$\pm 1 \sigma$ along each axis and centered at their average values 
for C-O and C-O-Ne.
}
\end{figure}

Figure \ref{fig:masshighdens} compares the final yield of IGE elements
for the C-O and C-O-Ne simulation suites with the amount of expansion of the
WD during the deflagration phase. The amount of expansion is 
characterized by the mass above $2 \times 10^7~\grampercc$ at the 
time of the DDT, with more high-density mass
indicating less expansion during deflagration. The averages of both
the C-O and C-O-Ne suites along both axes are indicated by the shaded
regions with $\pm1\sigma$ widths.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/FMBTI_v_Ni56Yield_plot.pdf}
\caption{\label{fig:conversion}
Estimated yield of \Ni{56} as a function of final mass burned to IGE
for C-O-Ne progenitors (red) and C-O progenitors (blue) at
$t = 4.0 \second$.
}
\end{figure}
Figure \ref{fig:conversion} shows the estimated \Ni{56} yields 
across the range of masses burned to IGE
for all C-O and C-O-Ne realizations at the end 
of the simulations ($4.0 \second$),
at which point the total mass burned to \Ni{56} had become constant.
The difference between the two sets of results is more pronounced
than the difference between hybrid and tradition models
found by \citet{willcoxetal2016}. This difference follows from
differences in the electron capture rates, which follow from
{\color{red} two} reasons. {\color{red} HIGHER CENTRAL DENSITY?
MORE METALLICIY? HELP!}
%The conversion of \Ni{56} to IGEs are more pronounced in my case. There are two assumptions as to why figure 6 is more pronounced in my paper then in Dons. 
%First is that higher critical density leads to higher electron capture resulting in less N\Ni{56}i56 produced. Figure 4 shows that CO model has a stronger electron capture then the hybrid model. The second is that the central ignition leads to early burning at higher density. Both of these cases lead to more electron capture resulting in a larger difference in evolution between the models.
%NEW: Production of 56Ni and mass burned to IGEs for CO (red) and
%hybrid CONe (green) WD realizations. SAME AS DON'S FIG 18

\begin{figure}
\includegraphics[width=\columnwidth]{figures/compare_ratio_v2.png}
\caption{\label{fig:compare_ratio}
Plot of estimated \Ni{56} mass vs.\ time showing the evolution
for both suites of simulations. Results from 
C-O-Ne progenitors are in red and C-O progenitors blue. 
{\color{red} SAME AS DON'S FIGURE 19}.
%SAME AS DON'S FIGURE 19
}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figures/compare_burned_mass_v2.png}
\caption{\label{fig:compare_burned}
Plot of estimated mass burned to IGEs vs.\ time showing the evolution
for both suites of simulations. Results from C-O-Ne progenitors are 
in red and C-O progenitors blue.  
Note that one of the C/O simulations presented did not complete.
%SAME AS DON'S FIGURE 20
{\color{red} SAME AS DON'S FIGURE 20.} 
}
\end{figure}

Figure \ref{fig:compare_ratio} shows the fraction by mass of IGE
material producing \Ni{56} as it evolves in time and Figure
\ref{fig:compare_burned} shows the concurrent evolution of mass
burned to IGE for both suites. While there is considerable
scatter in the results, differences are obvious.

During the deflagration phase, the C-O models
on average burn more material to IGE and also had a significantly higher
fraction of IGE material that is \Ni{56}, yielding more \Ni{56} than
the C-O-Ne models. This result is counter to that observed in
\citet{willcoxetal2016}. During the detonation phase, the differences
are not as obvious and the final mass of IGEs are comparable. The
fraction of IGE material that is \Ni{56} at the end of the evolution,
however, is significantly higher. This result differs from 
the results of \citet{willcoxetal2016} as well.

We attribute these differences as following from the different
compositions of the progenitors. The C-O-Ne hybrid progenitors
had more more neutron-rich material (a lower $Y_e$) than the
traditional C-O models. As expected, when this material burns
to IGEs, the proportion of neutron-rich material only gets
higher, as the results demonstrate.

The difference between these results and those of \citet{willcoxetal2016}
follows from the hybrid C-O-Ne progenitors having a different
temperature structure that led to ignition of the explosion at lower
densities. The C-O models in the \citet{willcoxetal2016} study
thus had more material burning at high densities and thus more
neutronization and a lower relative \Ni{56} yield than the
hybrid C-O-Ne models. In the case of the comparison here, the
C-O and hybrid C-O-Ne models {\color{red} the same central 
temperature and density and very similar temperature and density 
profiles at high densities, so the simulations in both cases 
began with central ignitions. Differences in the explosion outcome 
accordingly follow from differences in the composition.}

@@

Below Rough:

The new generation of C-O-Ne hybrid progenitor models explode similarly to
traditional C-O models. We conclude they are viable progenitors.

The new generation of C-O-Ne hybrid progenitor models yield
slightly less \Ni{56}, which is actually in keeping with how
the C-O models compare to observations. Our C-O models tend
to produce enough \Ni{56} to imply bright events.

More.....
